### 2019-09-21 README.Rmd
added to discussion points

- Should I write the code in a package or just save the functions in a folder in the paper repository?
- Sometimes LIME does not want to run in R with the bullet data

>>>>

- Should I write the code in a package or just save the functions in a folder in the paper repository?
- MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
- How to handle the issue of accessing the perturbations?
- Do we want to think of a metric that is stand alone? - not just for comparisons
- Sometimes LIME does not want to run in R with the bullet data - this example works but I'm running into issues with the package...I don't really understand how the predict_model functions work
